### 2025-08-12 draft.qmd
20250809 - add cost
20250812 - draft tools

FantasyFootballAnalytics.net provides tools to help you win your [snake draft](#sec-draftSnake): <https://fantasyfootballanalytics.net/win-your-snake-draft>.
For draft tools for [snake drafts](#sec-draftSnake), see the Fantasy Football Analytics web application: <https://apps.fantasyfootballanalytics.net>.
The web application includes a free tool that allows users to specify their custom league settings to calculate projected points that are customized to their league and helps users select which players to draft that maximize the players' [value over replacement players](#sec-fantasyValueVORP) (VORP).

@@

FantasyFootballAnalytics.net provides tools to help you win your [auction draft](#sec-draftSnake) (<https://fantasyfootballanalytics.net/how-to-win-your-auction-draft>) and daily fantasy sports (DFS) leagues (<https://fantasyfootballanalytics.net/how-to/dfsoptimizerhelp>).
For draft and player selection tools for [auction drafts](#sec-draftSnake) and DFS leagues, see the Fantasy Football Analytics web application: <https://apps.fantasyfootballanalytics.net>.
The web application includes a free tool that allows users to specify their custom league settings to calculate projected points that are customized to their league, and to identify the optimal lineup given their league settings and salary cap.

@@

```{r}
mostRecentProjections[which(sol$solution == 1), c("name","pos","points")]
```

>>>>

FantasyFootballAnalytics.net provides tools to help you win your [snake draft](#sec-draftSnake): <https://fantasyfootballanalytics.net/win-your-snake-draft>.
For draft tools for [snake drafts](#sec-draftSnake), see the Fantasy Football Analytics web application (depicted in @fig-snakeDraftToolFFA): <https://apps.fantasyfootballanalytics.net>.
The web application includes a free tool that allows users to specify their custom league settings to calculate projected points that are customized to their league and helps users select which players to draft that maximize the players' [value over replacement players](#sec-fantasyValueVORP) (VORP).

::: {#fig-snakeDraftToolFFA}
![](images/snakeDraftTool.png){fig-alt="Free Snake Draft Tool From Fantasy Football Analytics. From <https://apps.fantasyfootballanalytics.net>."}

Free Snake Draft Tool From Fantasy Football Analytics. From <https://apps.fantasyfootballanalytics.net>.
:::

@@

FantasyFootballAnalytics.net provides tools to help you win your [auction draft](#sec-draftSnake) (<https://fantasyfootballanalytics.net/how-to-win-your-auction-draft>) and daily fantasy sports (DFS) leagues (<https://fantasyfootballanalytics.net/how-to/dfsoptimizerhelp>).
For draft and player selection tools for [auction drafts](#sec-draftSnake) and DFS leagues, see the Fantasy Football Analytics web application (depicted in @fig-auctionDraftToolFFA): <https://apps.fantasyfootballanalytics.net>.
The web application includes a free tool that allows users to specify their custom league settings to calculate projected points that are customized to their league, and to identify the optimal lineup given their league settings and salary cap.

::: {#fig-auctionDraftToolFFA}
![](images/lineupOptimizer.png){fig-alt="Free Auction Draft Lineup Optimizer From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>."}

Free Auction Draft Lineup Optimizer From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>.
:::

@@

```{r}
mostRecentProjections[which(sol$solution == 1), c("name","pos","cost","points")]
```
